---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
runtime: shiny
---

```{r , include=FALSE}

#install.packages("flexdashboard")
#install.packages("DT")
  library(flexdashboard)
  library(jsonlite)
  library(dplyr)
  library(ggplot2)
  library(highcharter)
  library(geojsonio)
  library(lubridate)
  library(tabulizer)
  library(stringr)
  library(gsubfn)
  library(DT)

```


```{r, include=FALSE}
car_makes <- c("ACURA","AM GENERAL","AMERICAN IRONHORSE","APRILIA","ARCTIC CAT","ASTON MARTIN","ATK","AUDI","AVANTI","BENTLEY","BIG DOG","BIMOTA","BLUE BIRD","BMW","BOMBARDIER","BUELL","BUICK","CADILLAC","CANNONDALE","CHANCE COACH TRANSIT BUS","CHEVROLET","CHRYSLER","COBRA","DAEWOO","DODGE","DUCATI","E-TON","EL DORADO","FERRARI","FORD","FREIGHTLINER","GAS GAS","GILLIG","GMC","HARLEY DAVIDSON","HINO","HM","HONDA","HUSABERG","HUSQVARNA","HYUNDAI","INDIAN","INFINITI","INTERNATIONAL","ISUZU","JAGUAR","JEEP","KAWASAKI","KENWORTH","KIA","KTM","KYMCO","LAFORZA","LAMBORGHINI","LANDROVER","LEXUS","LINCOLN","LOTUS","MACK","MAZDA","MERCEDES-BENZ","MERCURY","MITSUBISHI","MITSUBISHI FUSO","MOTO GUZZI","MOTOR COACH INDUSTRIES","MV AGUSTA","NEW FLYER","NISSAN","NOVA BUS CORPORATION","OLDSMOBILE","ORION BUS","OSHKOSH MOTOR TRUCK CO.","OTTAWA","PANOZ","PETERBILT","PEUGEOT","PLYMOUTH","POLARIS","PONTIAC","PORSCHE","QVALE","RENAULT","ROLLS ROYCE","SAAB","SATURN","SEA-DOO","SEAT","SKI-DOO","STERLING","STERLING TRUCK","SUBARU","SUZUKI","TM","TOYOTA","TRIUMPH","UD","VICTORY","VOLKSWAGEN","VOLVO","WESTERN STAR","WORKHORSE","YAMAHA","ALFA ROMEO","AUTOCAR LLC.","COUNTRY COACH MOTORHOME","HUMMER","KASEA","LEM","MASERATI","MINI","MORGAN","SALEEN","WESTERN RV","MAYBACH","ROVER","VENTO","FIAT","JOHN DEERE","KUBOTA","SCION","SMART","VESPA","HYOSUNG","PIAGGIO","ARGO","BUGATTI","PIERCE MFG. INC.","AMERICAN LAFRANCE","CAN-AM","CRANE CARRIER","CUB CADET","BETA","BOBCAT","TESLA","RAM","VPG","CODA","FISKER","MCLAREN","SRT","BERTONE","IC CORPORATION","NASH")
```


```{r Feature extaction, include=FALSE}




# The goal here is to run through all the folders and subfolders, read each PDF, extract the key features, and store into a data frame


File_Name <- character()
Vehicle_make <- character()
Error_code_list <- list()
Error_text_list <-  list()
All_error_codes <- character()
All_error_texts <- character()



# Feature extraction

i=1

for (file_name in dir(path = "./Inputs/PDF/",pattern = "^.*Diagnostic.*\\.pdf",full.names=TRUE,recursive=TRUE)){
  

  
  #Extract text from PDF
  out_text <- extract_text(file_name)
  #Basic text cleansing to enmable text recognition
  out_text <- gsub("\\","", out_text,fixed=TRUE)
  out_text_words <- unique(strsplit(paste(out_text, collapse = " "), ' ')[[1]])
  out_text_words <- gsub("\r","",out_text_words)
  out_text_words <- gsub("\n","",out_text_words)
  
  #Extract feature from cleansed text

  error_codes <- as.vector(unique (grep(".....\\-\\d\\d", out_text_words, value=TRUE)))
  car_make <- ifelse(length(intersect(out_text_words,car_makes)) == 0,"Not found",intersect(out_text_words,car_makes)) # to avoid zero length error
  error_texts <- as.vector(unique(strapplyc(out_text, ".....\\-\\d\\d(.*?)(\r\n|\r|\n).*", simplify = c)))
  
  
  
  File_Name[i] <- file_name
  Vehicle_make[i] <- car_make
  Error_code_list[[length(Error_code_list)+1]] <- error_codes
  Error_text_list[[length(Error_text_list)+1]] <- error_texts
  All_error_codes <- c(All_error_codes,error_codes)
  All_error_texts <- c(All_error_texts,error_texts)
  
  
  i <- i+1
  
}

features_df <- data.frame(cbind(File_Name,Vehicle_make,Error_code_list,Error_text_list))


```


```{r Selectors choices prep}

car_makes_list <- c("ACURA","AM GENERAL","AMERICAN IRONHORSE","APRILIA","ARCTIC CAT","ASTON MARTIN","ATK","AUDI","AVANTI","BENTLEY","BIG DOG","BIMOTA","BLUE BIRD","BMW","BOMBARDIER","BUELL","BUICK","CADILLAC","CANNONDALE","CHANCE COACH TRANSIT BUS","CHEVROLET","CHRYSLER","COBRA","DAEWOO","DODGE","DUCATI","E-TON","EL DORADO","FERRARI","FORD","FREIGHTLINER","GAS GAS","GILLIG","GMC","HARLEY DAVIDSON","HINO","HM","HONDA","HUSABERG","HUSQVARNA","HYUNDAI","INDIAN","INFINITI","INTERNATIONAL","ISUZU","JAGUAR","JEEP","KAWASAKI","KENWORTH","KIA","KTM","KYMCO","LAFORZA","LAMBORGHINI","LANDROVER","LEXUS","LINCOLN","LOTUS","MACK","MAZDA","MERCEDES-BENZ","MERCURY","MITSUBISHI","MITSUBISHI FUSO","MOTO GUZZI","MOTOR COACH INDUSTRIES","MV AGUSTA","NEW FLYER","NISSAN","NOVA BUS CORPORATION","OLDSMOBILE","ORION BUS","OSHKOSH MOTOR TRUCK CO.","OTTAWA","PANOZ","PETERBILT","PEUGEOT","PLYMOUTH","POLARIS","PONTIAC","PORSCHE","QVALE","RENAULT","ROLLS ROYCE","SAAB","SATURN","SEA-DOO","SEAT","SKI-DOO","STERLING","STERLING TRUCK","SUBARU","SUZUKI","TM","TOYOTA","TRIUMPH","UD","VICTORY","VOLKSWAGEN","VOLVO","WESTERN STAR","WORKHORSE","YAMAHA","ALFA ROMEO","AUTOCAR LLC.","COUNTRY COACH MOTORHOME","HUMMER","KASEA","LEM","MASERATI","MINI","MORGAN","SALEEN","WESTERN RV","MAYBACH","ROVER","VENTO","FIAT","JOHN DEERE","KUBOTA","SCION","SMART","VESPA","HYOSUNG","PIAGGIO","ARGO","BUGATTI","PIERCE MFG. INC.","AMERICAN LAFRANCE","CAN-AM","CRANE CARRIER","CUB CADET","BETA","BOBCAT","TESLA","RAM","VPG","CODA","FISKER","MCLAREN","SRT","BERTONE","IC CORPORATION","NASH")

error_code_list <- Error_code_list


```




Column {.sidebar}
-----------------------------------------------------------------------

Select period, operators and terminals below :


```{r Car Make selection}


      selectizeInput("car_make_selection", label = "Car Make:",
                        choices = car_makes_list, selected = "BMW",
                     options = list(maxItems = 3, placeholder = 'please enter make here',multiple = TRUE))

```

```{r Error code selection}
      selectInput("error_code_selection", label = "Error Code:",
                  choices = All_error_codes, selected = NULL,
                  options = list(maxItems = 3, placeholder = 'please enter error codes here',multiple = TRUE))

```

```{r Error text selection }

  selectizeInput("error_text_selection",label = "Error Text:",
                  choices = All_error_texts , selected = NULL,
                 options = list(maxItems = 3, placeholder = 'please enter error text here',multiple = TRUE))

```





Column   
-----------------------------------------------------------------------

### List of relevant files


```{r Build table corresponding to search terms}

# Handle cases when selection is blank

build_query_result_table <- function(input_make_selection,input_error_code_selection,input_error_text_selection){
  
  if(length(input_make_selection) == 0){
    
        query_result_table <- features_df %>% 
           filter(input$car_make_selection == Vehicle_make &&
           input$error_code_selection %in% Error_code_list &&
           input$error_text_selection %in% Error_text_list)
    
  }
  
  if(length(input_make_selection) == 0){
    
        query_result_table <- features_df %>% 
           filter(input$car_make_selection == Vehicle_make &&
           input$error_code_selection %in% Error_code_list &&
           input$error_text_selection %in% Error_text_list)
    
  }
  
  if(length(input_make_selection) == 0){
    
        query_result_table <- features_df %>% 
           filter(input$car_make_selection == Vehicle_make &&
           input$error_code_selection %in% Error_code_list &&
           input$error_text_selection %in% Error_text_list)
    
  }
  
  
}
renderDataTable({

  #Subset data frame based on user selection  
  
  

 
 
 # Build and Display in DT
 
 dt <- datatable(query_result_table)
 
 return(dt)
 

})

