---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
runtime: shiny
---

```{r , include=FALSE}

  #library(rJava)
  library(flexdashboard)
  library(dplyr)
  library(ggplot2)
  library(lubridate)
  library(tabulizer)
  library(stringr)
  library(gsubfn)
  library(DT)
  library(stringr)

```


```{r, include=FALSE}
car_makes <- c("ACURA","AM GENERAL","AMERICAN IRONHORSE","APRILIA","ARCTIC CAT","ASTON MARTIN","ATK","AUDI","AVANTI","BENTLEY","BIG DOG","BIMOTA","BLUE BIRD","BMW","BOMBARDIER","BUELL","BUICK","CADILLAC","CANNONDALE","CHANCE COACH TRANSIT BUS","CHEVROLET","CHRYSLER","COBRA","DAEWOO","DODGE","DUCATI","E-TON","EL DORADO","FERRARI","FORD","FREIGHTLINER","GAS GAS","GILLIG","GMC","HARLEY DAVIDSON","HINO","HM","HONDA","HUSABERG","HUSQVARNA","HYUNDAI","INDIAN","INFINITI","INTERNATIONAL","ISUZU","JAGUAR","JEEP","KAWASAKI","KENWORTH","KIA","KTM","KYMCO","LAFORZA","LAMBORGHINI","LANDROVER","LEXUS","LINCOLN","LOTUS","MACK","MAZDA","MERCEDES-BENZ","MERCURY","MITSUBISHI","MITSUBISHI FUSO","MOTO GUZZI","MOTOR COACH INDUSTRIES","MV AGUSTA","NEW FLYER","NISSAN","NOVA BUS CORPORATION","OLDSMOBILE","ORION BUS","OSHKOSH MOTOR TRUCK CO.","OTTAWA","PANOZ","PETERBILT","PEUGEOT","PLYMOUTH","POLARIS","PONTIAC","PORSCHE","QVALE","RENAULT","ROLLS ROYCE","SAAB","SATURN","SEA-DOO","SEAT","SKI-DOO","STERLING","STERLING TRUCK","SUBARU","SUZUKI","TM","TOYOTA","TRIUMPH","UD","VICTORY","VOLKSWAGEN","VOLVO","WESTERN STAR","WORKHORSE","YAMAHA","ALFA ROMEO","AUTOCAR LLC.","COUNTRY COACH MOTORHOME","HUMMER","KASEA","LEM","MASERATI","MINI","MORGAN","SALEEN","WESTERN RV","MAYBACH","ROVER","VENTO","FIAT","JOHN DEERE","KUBOTA","SCION","SMART","VESPA","HYOSUNG","PIAGGIO","ARGO","BUGATTI","PIERCE MFG. INC.","AMERICAN LAFRANCE","CAN-AM","CRANE CARRIER","CUB CADET","BETA","BOBCAT","TESLA","RAM","VPG","CODA","FISKER","MCLAREN","SRT","BERTONE","IC CORPORATION","NASH")
```


```{r Feature extaction, include=FALSE}

# The goal here is to run through all the folders and subfolders, read each PDF, extract the key features, and store into a data frame


File_Name <- character()
Vehicle_make <- character()
Error_code_list <- character()
Error_text_list <-  character()
All_error_codes <- character()
All_error_texts <- character()
VIN_number <- character()
Reg_number <- character()
Date_diagnostic <- .POSIXct(character())




# Feature extraction

i=1

for (file_name in dir(path = "./Inputs/PDF/",pattern = "^.*Diagnostic.*\\.pdf",full.names=TRUE,recursive=TRUE)){
  

  
  #Extract text from PDF
  out_text <- extract_text(file_name)
  #Basic text cleansing to enmable text recognition
  out_text <- gsub("\\","", out_text,fixed=TRUE)
  out_text_words <- unique(strsplit(paste(out_text, collapse = " "), ' ')[[1]])
  out_text_words <- gsub("\r","",out_text_words)
  out_text_words <- gsub("\n","",out_text_words)
  
  #Extract feature from cleansed text

  error_codes <- as.vector(unique (grep("[A-Z]....\\-\\d\\d", out_text_words, value=TRUE))) # First pattern for error codes
  error_codes_add <- as.vector(unique (grep("[A-Z]\\d\\d\\d", out_text_words, value=TRUE))) # Another pattern for error codes
  error_codes_add <- error_codes_add[nchar(error_codes_add)==5] #Removing incorrect matched for pattern 2
  error_codes <- c(error_codes,error_codes_add) # Merging into a single vector
  
  #Retrieveing car make
  car_make <- ifelse(length(intersect(out_text_words,car_makes)) == 0,
                     "Not found",
                     intersect(out_text_words,car_makes)) # to avoid zero length error
  
  #Retrieving error text and code lists
  error_texts <- as.vector(
    unique(
      strapplyc(out_text, "[A-Z]....\\-\\d\\d(.*?)(\r\n|\r|\n).*", simplify = c))) # Assumes 1st char error code is letter
  
  #error_texts <- ifelse(length(error_texts)==0,"NA",error_texts)
  #error_codes <- ifelse(length(error_codes)==0,"NA",error_codes)
  error_texts <- error_texts[nchar(error_texts)>2] # Retaining only elements with at least 3 characters
  
  #Retrieve VIN number
  VIN_number_text <- as.vector(
    unique(
      strapplyc(out_text, "VIN:(.*?)(\r\n|\r|\n).*", simplify = c))) # Regex would need improving to avoid next line
  
  VIN_number_text <- VIN_number_text[nchar(VIN_number_text)>2]
  VIN_number[i] <- ifelse(length(VIN_number_text) == 0,"NA",VIN_number_text)
  
  #Registration plate number
  
  
  Reg_number_text <- as.vector(
    unique(
      strapplyc(out_text, "License #:(.*?)(\r\n|\r|\n).*", simplify = c)))
  
  Reg_number_text <- Reg_number_text[1]
  Reg_number_text <- ifelse(is.na(Reg_number_text) ,
                            "Not found",
                            Reg_number_text) #If the Reg is not in the file it may be in the file name
  
  
  # Date and time of diagnostic
  test_time_text <- as.vector(unique(strapplyc(out_text, "Test Time: (.*?)(\r\n|\r|\n).*", simplify = c)))
  test_time_text <- test_time_text[nchar(test_time_text) >2]
  test_time_text <- as.POSIXct(test_time_text,format = "%Y-%m-%d %H:%M:%S")


  
  
  
  File_Name[i] <- file_name
  Vehicle_make[i] <- car_make
  Date_diagnostic[i] <- test_time_text
  Reg_number[i] <- Reg_number_text
  Error_code_list[i] <- paste(error_codes,collapse = "")
  Error_text_list[i] <- paste(error_texts,collapse = "")
  All_error_codes <- c(All_error_codes,error_codes)
  All_error_texts <- c(All_error_texts,error_texts)
  
  
  i <- i+1
  
}


features_df <- cbind(File_Name,Vehicle_make,VIN_number,Error_code_list,Error_text_list,Reg_number)
features_df <- as.data.frame(features_df)
features_df$Diagnostic_time <- Date_diagnostic


```


```{r Selectors choices prep}

car_makes_list <- c("ACURA","AM GENERAL","AMERICAN IRONHORSE","APRILIA","ARCTIC CAT","ASTON MARTIN","ATK","AUDI","AVANTI","BENTLEY","BIG DOG","BIMOTA","BLUE BIRD","BMW","BOMBARDIER","BUELL","BUICK","CADILLAC","CANNONDALE","CHANCE COACH TRANSIT BUS","CHEVROLET","CHRYSLER","COBRA","DAEWOO","DODGE","DUCATI","E-TON","EL DORADO","FERRARI","FORD","FREIGHTLINER","GAS GAS","GILLIG","GMC","HARLEY DAVIDSON","HINO","HM","HONDA","HUSABERG","HUSQVARNA","HYUNDAI","INDIAN","INFINITI","INTERNATIONAL","ISUZU","JAGUAR","JEEP","KAWASAKI","KENWORTH","KIA","KTM","KYMCO","LAFORZA","LAMBORGHINI","LANDROVER","LEXUS","LINCOLN","LOTUS","MACK","MAZDA","MERCEDES-BENZ","MERCURY","MITSUBISHI","MITSUBISHI FUSO","MOTO GUZZI","MOTOR COACH INDUSTRIES","MV AGUSTA","NEW FLYER","NISSAN","NOVA BUS CORPORATION","OLDSMOBILE","ORION BUS","OSHKOSH MOTOR TRUCK CO.","OTTAWA","PANOZ","PETERBILT","PEUGEOT","PLYMOUTH","POLARIS","PONTIAC","PORSCHE","QVALE","RENAULT","ROLLS ROYCE","SAAB","SATURN","SEA-DOO","SEAT","SKI-DOO","STERLING","STERLING TRUCK","SUBARU","SUZUKI","TM","TOYOTA","TRIUMPH","UD","VICTORY","VOLKSWAGEN","VOLVO","WESTERN STAR","WORKHORSE","YAMAHA","ALFA ROMEO","AUTOCAR LLC.","COUNTRY COACH MOTORHOME","HUMMER","KASEA","LEM","MASERATI","MINI","MORGAN","SALEEN","WESTERN RV","MAYBACH","ROVER","VENTO","FIAT","JOHN DEERE","KUBOTA","SCION","SMART","VESPA","HYOSUNG","PIAGGIO","ARGO","BUGATTI","PIERCE MFG. INC.","AMERICAN LAFRANCE","CAN-AM","CRANE CARRIER","CUB CADET","BETA","BOBCAT","TESLA","RAM","VPG","CODA","FISKER","MCLAREN","SRT","BERTONE","IC CORPORATION","NASH")

error_code_list <- Error_code_list


```




Column {.sidebar}
-----------------------------------------------------------------------

Select period, operators and terminals below :


```{r Car Make selection}


      selectizeInput("car_make_selection", label = "Car Make:",
                     choices = car_makes_list,multiple = TRUE)

```

```{r Error code selection}

      selectizeInput("error_code_selection", label = "Error Code:",
                  choices = All_error_codes, multiple = TRUE)

```

```{r Error text selection }

      selectizeInput("error_text_selection",label = "Error Text:",
                  choices = All_error_texts ,multiple = TRUE)

```





Column   
-----------------------------------------------------------------------

### List of relevant files


```{r Build table corresponding to search terms}

# Handle cases when selection is blank

build_query_result_table <- function(input_make_selection,input_error_code_selection,input_error_text_selection){
  
  len_make <- ifelse(is.null(input_make_selection) ,0,1)
  len_error_code <-  ifelse(is.null(input_error_code_selection) ,0,1)
  len_error_text <-  ifelse(is.null(input_error_text_selection) ,0,1)
  
  #---------
  #Accounting for blak fields
  
  if(len_make == 0 && len_error_code == 0 && len_error_text ==0 ){
  
  query_result_table <- features_df
      
  #,Reg_number
  
  
  }
  
  if(len_make == 0 & len_error_code == 0 & len_error_text >0 ){
  
    query_result_table <- features_df %>% 
      filter(str_detect(Error_text_list,paste(input_error_text_selection,collapse = '|')))
  #,Reg_number
  
  
  }
  
  if(len_make == 0 && len_error_code > 0 && len_error_text == 0 ){
  
    query_result_table <- features_df %>% 
      filter(str_detect(Error_code_list,paste(input_error_code_selection,collapse = '|')))
  #,Reg_number
  
  }
  
  if(len_make > 0 && len_error_code > 0 && len_error_text == 0 ){
  
    query_result_table <- features_df %>% 
      filter(str_detect(Vehicle_make,paste(input_make_selection,collapse = '|')) &
           str_detect(Error_code_list,paste(input_error_code_selection,collapse = '|')))
  #,Reg_number
  
  
  }
  
  if(len_make > 0 && len_error_code == 0 && len_error_text > 0 ){
  
    query_result_table <- features_df %>% 
      filter(str_detect(Vehicle_make,paste(input_make_selection,collapse = '|')) &
           str_detect(Error_text_list,paste(input_error_code_selection,collapse = '|')))
  
  }
  
  
  if(len_make > 0 && len_error_code == 0 && len_error_text == 0 ){
  
    query_result_table <- features_df %>% 
      filter(str_detect(Vehicle_make,paste(input_make_selection,collapse = '|')))%>% 
      select(File_Name,Vehicle_make,Diagnostic_time) %>% 
      as.data.frame()
  #,Reg_number
  
  }
  
  
   if(len_make == 0 && len_error_code > 0 && len_error_text > 0 ){
  
    query_result_table <- features_df %>% 
    filter(str_detect(Error_text_list,paste(input_error_text_selection,collapse = '|')) &
           str_detect(Error_code_list,paste(input_error_code_selection,collapse = '|')))
  
  }
  
  
  if(len_make > 0 && len_error_code > 0 && len_error_text > 0 ){
  
    query_result_table <- features_df %>% 
    filter(str_detect(Vehicle_make,paste(input_make_selection,collapse = '|')) &
           str_detect(Error_text_list,paste(input_error_text_selection,collapse = '|')) &
           str_detect(Error_code_list,paste(input_error_code_selection,collapse = '|')))
  
  }
  
  
  #url_prefix = "https://www.dropbox.com/home/THEAA/Shared with me/"
  url_prefix <- "./Inputs/PDF/"
  
  query_result_table <- query_result_table %>% 
    #mutate(LinkToFile =paste0("<a href = '","Diagnostic Report sn09nxv.pdf","'>","Open file", "</a>"))
    #mutate(linktofile = a("click on me",href="Diagnostic Report sn09nxv.pdf"))
    mutate(linktofile  = "<a href='Diagnostic Report sn09nxv.pdf' target='blank' >MyFile</a>")
           
  return(query_result_table)
  
}


renderDataTable({

  #Subset data frame based on user selection  
  
  query_result_table <- build_query_result_table(input$car_make_selection,input$error_code_selection, input$error_text_selection) 
  
 
 # Build and Display in DT
 
 dt <- datatable(query_result_table,escape = FALSE)
 
 return(dt)
 

})

